---
title: "ChIP-Seq Data Analysis Report"
author: "ChIP-Seq Analysis Workflow"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    css: ["report.css", "common/assets/logo.css"]
    includes:
      in_header: common/logo/header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load required libraries
library(knitr)
library(DT)
library(plotly)
```

# ChIP-Seq Data Analysis Workflow

## Overview

This document summarizes the ChIP-Seq data analysis workflow and presents key results from the analysis pipeline.

## Data Processing

### Quality Control

```{r quality-control, eval=FALSE}
# Example quality control commands
# These would typically be run in the command line or as part of a pipeline

# FastQC for quality assessment
system("fastqc *.fastq.gz -o ../results/fastqc/")

# Trimming with Trimmomatic
system("trimmomatic PE input_R1.fastq.gz input_R2.fastq.gz 
       output_R1_paired.fastq.gz output_R1_unpaired.fastq.gz 
       output_R2_paired.fastq.gz output_R2_unpaired.fastq.gz 
       ILLUMINACLIP:TruSeq3-PE.fa:2:30:10 LEADING:3 TRAILING:3 SLIDINGWINDOW:4:15 MINLEN:36")
```

### Alignment

```{r alignment, eval=FALSE}
# Alignment with BWA or Bowtie2
system("bwa mem -t 8 reference_genome.fa trimmed_R1.fastq.gz trimmed_R2.fastq.gz | 
        samtools sort -o aligned_sorted.bam")

# Index BAM files
system("samtools index aligned_sorted.bam")
```

### Peak Calling

```{r peak-calling, eval=FALSE}
# Peak calling with MACS2
system("macs2 callpeak -t treatment.bam -c control.bam -f BAM -g hs -n sample_peaks --outdir ../results/peaks/")
```

## Results Summary

### Peak Statistics

```{r peak-stats, eval=FALSE}
# Load and summarize peak data
# This section would contain actual analysis code when data is available

cat("Peak calling results will be displayed here when data is processed.\n")
cat("Number of peaks identified: [To be calculated]\n")
cat("Average peak width: [To be calculated]\n")
cat("Peak distribution across chromosomes: [To be visualized]\n")
```

### Quality Metrics

```{r quality-metrics, eval=FALSE}
# Display quality control metrics
cat("FastQC summary results will be shown here.\n")
cat("Alignment statistics will be displayed here.\n")
```

## Visualization

### Peak Distribution

```{r peak-visualization, eval=FALSE}
# Create visualizations of peak distributions
# This would contain actual plotting code when data is available

plot(1:10, 1:10, main = "Placeholder for peak distribution plot", 
     xlab = "Genomic Position", ylab = "Peak Intensity")
```

## Conclusion

This analysis workflow provides a comprehensive approach to ChIP-Seq data processing, from raw data quality control through peak calling and visualization.

## Session Information

```{r session-info}
sessionInfo()
```